---
title: "Summary_of_Results"
author: "Bonni Beaupied and Sheena Martenies"
date: "7/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F)
#' Load required libraries
library(foreign)
library(stats)
library(splines)
library(mgcv)
library(tidyverse)
library(readxl)
library(writexl)
library(ggplot2)
library(ggcorrplot)
library(ggthemes)
library(nlme)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
options(scipen = 9999) #avoid scientific notation
```


```{r, echo = F}
dairy_data <- read_csv(here::here("Data", "Dairy_Data_Full.csv"))
```

## Distributions of outcome and predictor variables
Below are the histograms, scatter plots, and autocorrelation plots for the outcomes and predictor variables included in the dataset.

#### Average milk production (L) per day 
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = Avgmilk)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = Avgmilk)) +
  simple_theme

acf(dairy_data$Avgmilk, plot = T)
pacf(dairy_data$Avgmilk, plot = T)
```

#### Somatic Cell Counts
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = SCC_avg)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = SCC_avg)) +
  simple_theme

acf(dairy_data$SCC_avg, plot = T)
pacf(dairy_data$SCC_avg, plot = T)
```

#### Temperature-Humidity Index
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = THI)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = THI)) +
  simple_theme

acf(dairy_data$THI, plot = T, na.action = na.pass)
pacf(dairy_data$THI, plot = T, na.action = na.pass)
```


#### Ozone (ppb)
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = FOOTHILLS_DAILYMAXO3)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = FOOTHILLS_DAILYMAXO3)) +
  simple_theme

acf(dairy_data$FOOTHILLS_DAILYMAXO3, plot = T, na.action = na.pass)
pacf(dairy_data$FOOTHILLS_DAILYMAXO3, plot = T, na.action = na.pass)
```

#### Daily mean PM2.5 (ug/m3)
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = PM2.5_avg)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = PM2.5_avg)) +
  simple_theme

acf(dairy_data$PM2.5_avg, plot = T, na.action = na.pass)
pacf(dairy_data$PM2.5_avg, plot = T, na.action = na.pass)
```

#### Daily maximum PM2.5 (ug/m3)
```{r, echo = F}
ggplot(dairy_data) +
  geom_histogram(aes(x = PM2.5_max)) +
  simple_theme

ggplot(dairy_data) +
  geom_point(aes(x = DATE, y = PM2.5_max)) +
  simple_theme

acf(dairy_data$PM2.5_max, plot = T, na.action = na.pass)
pacf(dairy_data$PM2.5_max, plot = T, na.action = na.pass)
```

#### Correlations between each outcome and the predictor variables

```{r, echo = F}
var_cor <- select(dairy_data, -DATE) %>% 
  na.omit()
ggcorrplot(round(cor(var_cor), 1), outline.col = "white",
           lab = T, colors = c("#6D9EC1", "white", "#E46726"))
```

## Regression Analyses for Daily Production

We used two different modeling approaches to estimate the relationship between daily milk production and the environmental predictors: linear regression and generalized least squares with an autrocorrelation (AR1) structure.

#### Linear regression results

Model 0: Just date
```{r, echo = F}
prod_lm_0 <- lm(Avgmilk ~ DATE, data = dairy_data)
summary(prod_lm_0)
par(mfrow = c(2,2))
plot(prod_lm_0)
par(mfrow = c(1,1))
```

Model 1: Add THI
```{r, echo = F}
prod_lm_1 <- lm(Avgmilk ~ THI, data = dairy_data)
summary(prod_lm_1)
par(mfrow = c(2,2))
plot(prod_lm_1)
par(mfrow = c(1,1))
```

Model 2: Add ozone
```{r, echo = F}
prod_lm_2 <- lm(Avgmilk ~ THI + FOOTHILLS_DAILYMAXO3, data = dairy_data)
summary(prod_lm_2)
par(mfrow = c(2,2))
plot(prod_lm_2)
par(mfrow = c(1,1))
```

Model 3: Add daily mean PM2.5
```{r, echo = F}
prod_lm_3 <- lm(Avgmilk ~ THI + FOOTHILLS_DAILYMAXO3 + PM2.5_avg, 
              data = dairy_data)
summary(prod_lm_3)
par(mfrow = c(2,2))
plot(prod_lm_3)
par(mfrow = c(1,1))
```

Model 4: Swap for daily max pm2.5
```{r, echo = F}
prod_lm_4 <- lm(Avgmilk ~ THI + FOOTHILLS_DAILYMAXO3 + PM2.5_max, 
              data = dairy_data)
summary(prod_lm_4)
par(mfrow = c(2,2))
plot(prod_lm_4)
par(mfrow = c(1,1))
```

#### Generalized least squares regression results
Using a complete dataset:
```{r, echo = F}
dairy_data2 <- na.omit(dairy_data)
nrow(dairy_data2)
summary(dairy_data2)
```

Model 0: Just date
```{r, echo = F}
prod_0 <- gls(Avgmilk ~ DATE, data = dairy_data2,
               correlation = corAR1())
summary(prod_0)
plot(prod_0)
```

Model 1: Add THI
```{r, echo = F}
prod_1 <- gls(Avgmilk ~ DATE + THI, data = dairy_data2,
              correlation = corAR1())
summary(prod_1)
plot(prod_1)
```

Model 2: Add ozone
```{r, echo = F}
prod_2 <- gls(Avgmilk ~ DATE + THI + FOOTHILLS_DAILYMAXO3, data = dairy_data2,
              correlation = corAR1())
summary(prod_2)
plot(prod_2)
```

Model 3: Add daily mean PM2.5
```{r, echo = F}
prod_3 <- gls(Avgmilk ~ DATE + THI + FOOTHILLS_DAILYMAXO3 + PM2.5_avg, 
              data = dairy_data2,
              correlation = corAR1())
summary(prod_3)
plot(prod_3)
```

Model 4: Swap for daily max pm2.5
```{r, echo = F}
prod_4 <- gls(Avgmilk ~ DATE + THI + FOOTHILLS_DAILYMAXO3 + PM2.5_max, 
              data = dairy_data2,
              correlation = corAR1())
summary(prod_4)
plot(prod_4)
```

## Regression Analyses for Somatic Cell Counts

We used two different modeling approaches to estimate the relationship between daily somatic cell counts and the environmental predictors: linear regression and generalized least squares with an autrocorrelation (AR1) structure.

#### Linear regression results

Model 0: Just date
```{r, echo = F}
scc_lm_0 <- lm(SCC_avg ~ DATE, data = dairy_data)
summary(scc_lm_0)
par(mfrow = c(2,2))
plot(scc_lm_0)
par(mfrow = c(1,1))
```

Model 1: Add THI
```{r, echo = F}
scc_lm_1 <- lm(SCC_avg ~ THI, data = dairy_data)
summary(scc_lm_1)
par(mfrow = c(2,2))
plot(scc_lm_1)
par(mfrow = c(1,1))
```

Model 2: Add ozone
```{r, echo = F}
scc_lm_2 <- lm(SCC_avg ~ THI + FOOTHILLS_DAILYMAXO3, data = dairy_data)
summary(scc_lm_2)
par(mfrow = c(2,2))
plot(scc_lm_2)
par(mfrow = c(1,1))
```

Model 3: Add daily mean PM2.5
```{r, echo = F}
scc_lm_3 <- lm(SCC_avg ~ THI + FOOTHILLS_DAILYMAXO3 + PM2.5_avg, 
                data = dairy_data)
summary(scc_lm_3)
par(mfrow = c(2,2))
plot(scc_lm_3)
par(mfrow = c(1,1))
```

Model 4: Swap for daily max pm2.5
```{r, echo = F}
scc_lm_4 <- lm(SCC_avg ~ THI + FOOTHILLS_DAILYMAXO3 + PM2.5_max, 
                data = dairy_data)
summary(scc_lm_4)
par(mfrow = c(2,2))
plot(scc_lm_4)
par(mfrow = c(1,1))
```

#### Generalized least squares regression results

Model 0: Just date
```{r, echo = F}
scc_0 <- gls(SCC_avg ~ DATE, data = dairy_data2,
              correlation = corAR1())
summary(scc_0)
plot(scc_0)
```

Model 1: Add THI
```{r, echo = F}
scc_1 <- gls(SCC_avg ~ DATE + THI, data = dairy_data2,
              correlation = corAR1())
summary(scc_1)
plot(scc_1)
```

Model 2: Add ozone
```{r, echo = F}
scc_2 <- gls(SCC_avg ~ DATE + THI + FOOTHILLS_DAILYMAXO3, data = dairy_data2,
              correlation = corAR1())
summary(scc_2)
plot(scc_2)
```

Model 3: Add daily mean PM2.5
```{r, echo = F}
scc_3 <- gls(SCC_avg ~ DATE + THI + FOOTHILLS_DAILYMAXO3 + PM2.5_avg, 
             data = dairy_data2,
             correlation = corAR1())
summary(scc_3)
plot(scc_3)
```

Model 4: Swap for daily max pm2.5
```{r, echo = F}
scc_4 <- gls(SCC_avg ~ DATE + THI + FOOTHILLS_DAILYMAXO3 + PM2.5_max, 
             data = dairy_data2,
             correlation = corAR1())
summary(scc_4)
plot(scc_4)
```


